An Empirical Analysis of the Internet Engineering Task Force with Computational Methods

### 2024-10-06 paper.tex
Abstract

\documentclass[twocolumn,10pt]{article}
\pdfoutput=1 % This must be in the first 5 lines to tell arXiv to use pdfLaTeX
\usepackage[l2tabu,orthodox]{nag}
\usepackage[utf8x]{inputenc}
\usepackage[british]{babel}
\usepackage{microtype}
\usepackage{amsmath}
\usepackage[all]{onlyamsmath}
\usepackage{newtxtext}
\usepackage{newtxmath}
\usepackage[caption=false]{subfig}
\usepackage{booktabs}
\usepackage{upquote}
\usepackage{graphicx}
\usepackage{url}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{color}
\usepackage[cm]{fullpage}
\usepackage{multirow}
\usepackage{authblk}

@@

  The Internet requires interoperability between networks, systems, and
  applications, as well as cooperation among a growing number of
  stakeholders. The Internet Engineering Task Force (IETF) is critical in
  supporting this cooperation and interoperability by bringing together
  interested parties and standardising the protocols that power the
  Internet, such as IP or HTTP. Our work covers more 20 years of IETF
  data, and analyses the participants of the IETF, the emails they
  exchange, and the documents they produce. We show how these data can be
  used to understand who are these Internet actors, and their interests as
  well as how Internet's growth and maturity has given rise to a longer and
  complex standardisation process where participants gain and exercise
  influence and how this is reflected in the language they use and the
  interactions they have.

>>>>

\documentclass[twocolumn,10pt]{article}
\pdfoutput=1 % This must be in the first 5 lines to tell arXiv to use pdfLaTeX
\usepackage[l2tabu,orthodox]{nag}
\usepackage[utf8x]{inputenc}
\usepackage[british]{babel}
\usepackage{microtype}
\usepackage{amsmath}
\usepackage[all]{onlyamsmath}
\usepackage{newtxtext}
\usepackage{newtxmath}
\usepackage[caption=false]{subfig}
\usepackage{booktabs}
\usepackage{upquote}
\usepackage{graphicx}
\usepackage{url}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{color}
\usepackage[cm]{fullpage}
\usepackage{multirow}
\usepackage{authblk}
\usepackage{hyperref}

@@

  Technical operation of the Internet requires interoperability between
  networks, systems, and applications from different vendors as well as
  cooperation among a growing number of stakeholders. The Internet
  Engineering Task Force (IETF) is an open standards developing
  organisation that plays a critical role in enabling this cooperation and
  interoperability by bringing together interested parties to develop the
  protocols that power the Internet, such as IP or HTTP. In this paper, we
  review more 20 years of data about the IETF, studying who participates in
  the IETF, the emails they exchange, and the documents they produce. We
  show how these data can be used to understand who develops technical
  standards for the Internet, and their interests, and how Internet's
  growth and maturity has given rise to a longer and complex standards
  development process. We explore where participants gain and exercise
  influence, and how this is reflected in the language they use and in
  their interactions.

  This paper is a summary and collation of our prior published work,
  that can be found in full in:
  \cite{mcquistin:2021:characterising,khare:2022:web-we-weave,
  healey:2023:power,mcquistin:2023:errare,khare:2023:tracing,
  karan:2023:leda,healey:2023:power-frontiers,barnes:2024:temporal}.
